Issues with Dynamical Measurements Across the Disk

### 2019-02-15 paper/ms.tex
Add paragraph to conclusions

\begin{deluxetable*}{cccccccc}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun, using the relevant initial positions and velocities from \citet{2018AA...616A..10G}.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} & \colhead{neighborhood} \\ 
\colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$} & \colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 & 352\tablenotemark{b} & 57 \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 & 410\tablenotemark{c} & 1460 \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 & 112\tablenotemark{d} & 522\\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 & 400\tablenotemark{e} & 462 \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 & & \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 & & \\
NGC2451A\tablenotemark{a} & 193.7 & 5.8 & -1805 & 0.21 & 73.4 & & \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 & 800\tablenotemark{f} & 685 \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9 & 550\tablenotemark{d} & 781
\enddata

@@

\section{Conclusions}\label{sec:conclusion}
Let's conclude, shall we.

>>>>

\begin{deluxetable*}{cCCCCCCC}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun, using the relevant initial positions and velocities from \citet{2018AA...616A..10G}.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} & \colhead{neighborhood} \\ 
\colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$} & \colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 & 352\tablenotemark{b} & 57 \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 & 410\tablenotemark{c} & 1460 \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 & 112\tablenotemark{d} & 522\\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 & 400\tablenotemark{e} & 462 \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 & & \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 & & \\
NGC2451A\tablenotemark{a} & 193.7 & 5.8 & -1805 & 0.21 & 73.4 & & \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 & 800\tablenotemark{f} & 685 \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9 & 550\tablenotemark{d} & 781
\enddata

@@

\section{Conclusions}\label{sec:conclusion}
Actions have promise as excellent orbit labels. If the Galaxy can be
approximated as axisymmetric and 6D phase space positions can be measured
accurately and precisely enough, then the computed actions are invariant with
orbital phase. However, we hvae shown that the fact that the Galactic midplane
is not constant across the disk presents a significant complication to
computed actions actually being invariant. Our main conclusions are as
follows:
